\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2018-02-15 document/authorlist.tex
Last bursts and edits
Final draft sent around
Last updates before submission

\author{J.~Selsing\inst{1}
\and XSGRB collaboration
%\and D.~Malesani\inst{1}
%\and T.~Kr\"{u}hler\inst{1}
%\and J.~P.~U. Fynbo\inst{1}
%\and P.~Goldoni\inst{14}
%\and A.~de~Ugarte~Postigo\inst{11}
%\and J.~Japelj\inst{20}
%\and P.~D'Avanzo
%\and Z.~Cano
%\and S.~Covino\inst{10}
%\and V.~D'Elia\inst{712}
%\and H.~Flores
%\and O.~E.~Hartoog\inst{6}
%\and J.~Hjorth\inst{1}
%\and P.~Jakobsson\inst{5}
%\and A.~Levan
%\and A.~Melandri
%\and S.~Piranomonte \inst{7}
%\and R.~S\'anchez-Ram\'irez\inst{11}
%\and S.~Schulze\inst{1718}
%\and N.~R.~Tanvir\inst{19}
%\and C.~Th{\"o}ne
%\and S.~D.~Vergani\inst{78}
%\and P.~M.~Vreeswijk\inst{3}
%\and D.~J.~Watson\inst{1}
%\and K.~Wiersema\inst{19}
%\and D.~Xu\inst{1}
%\and L.~Christensen\inst{1}
%\and A.~De~Cia\inst{3}
%\and L.~Kaper\inst{6}
%\and L.~A.~Antonelli
%\and F.~Fiore
%\and A.~Gomboc
%\and P.~Groot
%\and F.~Hammer
%\and C.~Ledoux\inst{2}
%\and E.~Maiorano
%\and B.~Milvang-Jensen\inst{1}
%\and E.~Palazzi
%\and E.~Pian
%\and J.~Schaye
%\and G.~Tagliaferri\inst{7},
%\and R.~A.~M.~J.~Wijers\inst{6}
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark %1
%\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
%\and Department of Particle Physics and Astrophysics, Faculty of Physics, Weizmann Institute of Science, Rehovot 76100, Israel
%\and Th\"uringer Landessternwarte Tautenburg, Sternwarte 5, 07778 Tautenburg, Germany
%\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, IS-107 Reykjavik, Iceland
%\and Astronomical Institute Anton Pannekoek, University of Amsterdam, Science Park 904, NL-1098 XH Amsterdam, the Netherlands
%\and INAF-Osservatorio Astronomico di Roma, Via Frascati 33, I-00040 Monteporzio Catone, Italy
%\and GEPI-Observatoire de Paris, CNRS UMR 8111, Univ. Paris-Diderot, 5 Place Jules Janssen - 92190 Meudon, France
%\and American River College, Physics and Astronomy Dpt., 4700 College Oak Drive, Sacramento, CA 95841, USA
%\and INAF, Osservatorio Astronomico di Brera, Via E. Bianchi 46, I-23807 Merate, Italy
%\and Instituto de Astrof\'{\i}sica de Andaluc\'{\i}a (IAA-CSIC), Glorieta de la Astronom\'{\i}a s/n, 18008, Granada, Spain
%\and ASI-Science Data Centre, Via Galileo Galilei, I-00044 Frascati, Italy
%\and Institute of Experimental and Applied Physics, Czech Technical University in Prague, Horska 3a/22, 128 00 Prague 2, Czech Republic
%\and APC, Astroparticules et Cosmologie, Universite Paris Diderot, CNRS/IN2P3, CEA/Irfu, Observatoire de Paris, Sorbonne Paris Cite, 10, Rue Alice Domon et Leonie Duquet, 75205 Paris Cedex 13, France
%\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
%\and Universit\`a degli studi di Milano-Bicocca, Piazza della Scienza 3, 20126, Milano, Italy
%\and Pontificia Universidad Cat\'{o}lica de Chile, Departamento de Astronom\'{\i}a y Astrof\'{\i}sica, Casilla 306, Santiago 22, Chile
%\and Millennium Center for Supernova Science
%\and Department of Physics and Astronomy, University ofLeicester, University Road, Leicester, LE1 7RH, UK
%\and University of Ljubljana,Department of Physics,Faculty of Mathematics \& Physics,SI
}

>>>>

\author{
J.~Selsing \inst{1}$^,$\thanks{\email{jselsing@dark-cosmology.dk}}
\addtocounter{footnote}{2}
\and D.~Malesani \inst{1, 2, 3}\fnmsep\thanks{On-call observer}
\and P.~Goldoni \inst{4}\fnmsep$^\dagger$
\and J.~P.~U. Fynbo \inst{1, 2}\fnmsep$^\dagger$
\and T.~Kr\"{u}hler \inst{5}\fnmsep$^\dagger$
\and L.~A.~Antonelli \inst{6}\fnmsep$^\dagger$
\and M.~Arabsalmani \inst{7, 8}
\and J.~Bolmer \inst{5, 9}\fnmsep$^\dagger$
\and Z.~Cano \inst{10}\fnmsep$^\dagger$
\and L.~Christensen \inst{1}
\and S.~Covino \inst{11}\fnmsep$^\dagger$
\and P.~D'Avanzo \inst{11}\fnmsep$^\dagger$
\and V.~D'Elia \inst{12}\fnmsep$^\dagger$
\and A.~De~Cia \inst{13}
\and A.~de~Ugarte~Postigo \inst{1, 10}\fnmsep$^\dagger$
\and H.~Flores \inst{14}\fnmsep$^\dagger$
\and M.~Friis \inst{15, 16}
\and A.~Gomboc \inst{17}
\and J.~Greiner \inst{5}
\and P.~Groot \inst{18}
\and F.~Hammer \inst{14}
\and O.E.~Hartoog \inst{19}\fnmsep$^\dagger$
\and K.~E.~Heintz \inst{1, 2, 20}\fnmsep$^\dagger$
\and J.~Hjorth \inst{1}\fnmsep$^\dagger$
\and P.~Jakobsson \inst{20}\fnmsep$^\dagger$
\and J.~Japelj \inst{19}\fnmsep$^\dagger$
\and D.~A.~Kann \inst{10}\fnmsep$^\dagger$
\and L.~Kaper \inst{19}
\and C.~Ledoux \inst{9}
\and G.~Leloudas \inst{1}
\and A.J.~Levan \inst{21}\fnmsep$^\dagger$
\and E.~Maiorano \inst{22}
\and A.~Melandri \inst{11}\fnmsep$^\dagger$
\and B.~Milvang-Jensen \inst{1, 2}
\and E.~Palazzi \inst{22}
\and J.~T.~Palmerio \inst{23}\fnmsep$^\dagger$
\and D.~A.~Perley \inst{24}\fnmsep$^\dagger$
\and E.~Pian \inst{22}
\and S. ~Piranomonte \inst{6}\fnmsep$^\dagger$
\and G.~Pugliese \inst{19}\fnmsep$^\dagger$
\and R.~S\'{a}nchez-Ram\'{\i}rez \inst{25}\fnmsep$^\dagger$
\and S.~Savaglio \inst{26}
\and P.~Schady \inst{5}
\and S.~Schulze \inst{27}\fnmsep$^\dagger$
\and J.~Sollerman \inst{28}
\and M.~Sparre \inst{29}\fnmsep$^\dagger$
\and G.~Tagliaferri \inst{11}
\and N.~R.~Tanvir \inst{30}\fnmsep$^\dagger$
\and C.~C.~Th\"{o}ne \inst{10}
\and S.D.~Vergani \inst{14}\fnmsep$^\dagger$
\and P.~Vreeswijk \inst{18, 26}\fnmsep$^\dagger$
\and D.~Watson \inst{1, 2}\fnmsep$^\dagger$
\and K.~Wiersema \inst{21, 30}\fnmsep$^\dagger$
\and R.~Wijers \inst{19}
\and D.~Xu \inst{31}\fnmsep$^\dagger$
\and T.~Zafar \inst{32}
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark %1
%\and Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
\and The Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, 2800 Lyngby, Denmark
\and APC, Astroparticule et Cosmologie, Universit\'e Paris Diderot, CNRS/IN2P3, CEA/Irfu, Observatoire de Paris, Sorbonne Paris Cit\'e, 10, Rue Alice Domon et L\'eonie Duquet, 75205, Paris Cedex 13, France
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
\and INAF - Osservatorio Astronomico di Roma, Via Frascati 33, 00078, Monte Porzio Catone (Roma), Italy
\and IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France
\and Universit\'e Paris Diderot, AIM, Sorbonne Paris Cit\'e, CEA, CNRS, F-91191 Gif-sur-Yvette, France
\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain. % 10
%
\and INAF - Osservatorio Astronomico di Brera, via Bianchi 46, 23807, Merate (LC), Italy
\and Space Science Data Center - Agenzia Spaziale Italiana, via del Politecnico, s.n.c., I-00133, Roma, Italy
\and European Southern Observatory, Karl-Schwarzschild Str. 2, 85748 Garching bei M\”unchen, Germany
\and GEPI, Observatoire de Paris, PSL University, CNRS, 5 place Jules Janssen 92195, Meudon, France
\and KTH Royal Institute of Technology, Department of Physics, 106 91 Stockholm, Sweden
\and The Oskar Klein Centre for Cosmoparticle Physics, AlbaNova University Centre, 106 91 Stockholm, Sweden
\and Center for Astrophysics and Cosmology, University of Nova Gorica, Vipavska 11c, 5270 Ajdov\v s\v cina, Slovenia
\and Department of Astrophysics, IMAPP, Radboud University Nijmegen, PO Box 9010, 6500 GL Nijmegen, the Netherlands
\and Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, the Netherlands
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107, Reykjavik, Iceland
\and Department of Physics, University of Warwick, Coventry, CV4 7AL, UK % 20
%
\and IASF/INAF Bologna, via Piero Gobetti 101, 40129 Bologna, Italy
\and Sorbonne Universit\'e, CNRS, UMR7095, Institut d'Astrophysique de Paris, F-75014, Paris, France
\and Astrophysics Research Institute, Liverpool John Moores University, IC2, Liverpool Science Park, 146 Brownlow Hill, Liverpool L3 5RF, UK
\and INAF, Istituto Astrofisica e Planetologia Spaziali, Via Fosso del Cavaliere 100, I-00133 Roma, Italy
\and Physics Department, University of Calabria, I-87036 Arcavacata di Rende, Italy
\and Department of Particle Physics and Astrophysics, Weizmann Institute of Science, 234 Herzl Street, Rehovot, 761000, Israel
\and Department of Astronomy, Stockholm University, AlbaNova, 10691 Stockholm, Sweden 
\and Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, Karl-Liebknecht-Str.\,24/25, 14476 Golm, Germany
\and Department of Physics and Astronomy, University of Leicester, University Road, Leicester, LE1 7RH, United Kingdom
\and CAS Key Laboratory of Space Astronomy and Technology, National Astronomical Observatories, Chinese Academy of Sciences, Beijing, 100012, P.R. China % 30
%
\and Australian Astronomical Observatory, PO Box 915, North Ryde, NSW 1670, Australia.
}

### 2018-02-15 document/tables/sample_properties.tex
Last bursts and edits
Last updates before submission

\begin{table*}[!ht]
	\centering
	\begin{tabular}{cccc}
		\hline
		\hline\noalign{\smallskip}
		{} & {Full \textit{Swift} sample} & {Statistical sample} &  {Followed up bursts} \\
		\hline\noalign{\smallskip}
		N$_{BAT}$ & 987 & 156 & 89\\
		$\log(15-150$keV fluence)  & $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.7}^{+0.7}$   \\
		N$_{XRT}$ & 909 & 154 & 88\\
		$\log(0.3-10$keV flux) & $-12.3_{-0.8}^{+0.7}$ &  $-12.4_{-0.8}^{+0.7}$ &  $-12.4_{-0.7}^{+0.9}$  \\
		N$_{\mathrm{HI_x}}$ & 250 & 95 & 74\\
		$\log(\mathrm{N}_{\mathrm{HI_x}})$ & $21.7_{-0.9}^{+0.6}$ &  $21.5_{-3.4}^{+0.7}$ &  $21.6_{-4.5}^{+0.7}$  \\
		\hline\noalign{\smallskip}

@@

\caption{
	Population properties (median and 14th and 86th percentiles as the
	error intervals) for the \textit{Swift sample} and the subset of bursts
	fulfilling the sample criteria. The population characteristics of the three
	samples are very similar, which shows that our selection criteria effectively
	conserve the statistical properties of the underlying population, as least for
	these parameters.  Notice that not all bursts have measurements of the
	quantities we compare. \label{tab:sample_properties}
	}

>>>>

\begin{table*}[!ht]
	\centering
	\begin{tabular}{cccc}
		\hline
		\hline\noalign{\smallskip}
		{} & {Full \textit{Swift} sample} & {Statistical sample} &  {Followed up bursts} \\
		\hline\noalign{\smallskip}
		N$_{BAT}$ & 981 & 163 & 92\\
		$\log(15-150$ keV fluence)  & $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.6}^{+0.7}$ &  $-5.9_{-0.7}^{+0.7}$   \\
		N$_{XRT}$ & 902 & 160 & 90\\
		$\log(0.3-10$ keV flux) & $-12.3_{-0.8}^{+0.7}$ &  $-12.4_{-0.8}^{+0.7}$ &  $-12.4_{-0.7}^{+0.9}$  \\
		N$_{\mathrm{HI_x}}$ & 248 & 99 & 79\\
		$\log(\mathrm{N}_{\mathrm{HI_x}})$ & $21.7_{-0.9}^{+0.6}$ &  $21.5_{-3.4}^{+0.7}$ &  $21.6_{-4.5}^{+0.7}$  \\
		\hline\noalign{\smallskip}

@@

\caption{
	Population properties (median and 16th and 84th percentiles as the
	error intervals) for the \textit{Swift sample} and the subset of bursts
	fulfilling the sample criteria. The population characteristics of the three
	samples are very similar, which shows that our selection criteria effectively
	conserve the statistical properties of the underlying population, as least for
	these parameters.  Notice that not all bursts have measurements of the
	quantities we compare. \label{tab:sample_properties}
	}
